### 2023-08-25 main.tex
Fix 1

\subsection{Integrable process on a line segment}
{\color{red}Introduce integrable model here}

@@

In this section we specialize the multi-species stirring process to the geometry of the one dimensional chain with sites $\{1,\ldots,L\}$ where two reservoirs act at the boundary sites $1$ and $L$. These boundaries, exchanging particle with the external environment, put the chain out of equilibrium. The Hamiltonian that we consider here is obtained by \eqref{OriginalHamiltonian} assuming that the conductances are
    \omega_{x,y}=\begin{cases}
    1 \quad \text{if}\quad |x-y|=1\\
and the local inhomogeneities are
    \Gamma_{x}=\begin{cases}
        1\quad \text{if} \quad x\in \{1,L\}\\
We further assume that the maximal occupancy in each site is $\nu=1$, i.e. that there is an \textit{hard-core interaction}.
We will denote the element of the representation of the $gl(N)$ Lie algebra by lowercase letters, i.e. $(e_{ab})_{a,b\in\{1,\ldots,N\}}$, to highlight that we are in  the fundamental representation of the algebra.
The Hamiltonian is
\begin{equation}\label{hamiltonian}
	H=H_{left}+H_{bulk}+H_{right}
    H_{bulk}=\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}
Here $\mathcal{H}_{x,x+1}$  is a copy (acting on the edge $x,x+1$) of the two-site Hamiltonian
		\mathcal{H}=P-\id
with 
	P=\sum_{a,b=1}^Ne_{ab}\otimes e_{ba}.
The action of $\mathcal{H}$ amounts to the permutation of the occupations the two sites, i.e.
		\mathcal{H}|n\rangle\otimes   |m\rangle&=|m\rangle \otimes |n\rangle-|n\rangle \otimes|m\rangle
The boundary terms are given by 
	H_{left}=\begin{pmatrix}
		\alpha_{1}-1&\alpha_{1}&\alpha_{1}&\ldots&\ldots&\alpha_{1}\\
		\alpha_{2}&\alpha_{2}-1&\alpha_{2}&\ldots&\ldots&\alpha_{2}\\
		\vdots&\vdots& &\ddots& &\vdots\\
		\alpha_{N-1}&\alpha_{N-1}&\ldots&\ldots&\alpha_{N-1}-1&\alpha_{N-1}\\
		\alpha_{N}&\alpha_{N}&\ldots&\ldots&\alpha_{N}&\alpha_{N}-1
	H_{right}=\begin{pmatrix}
		\beta_{1}-1&\beta_{1}&\beta_{1}&\ldots&\ldots&\beta_{1}\\
		\beta_{2}&\beta_{2}-1&\beta_{2}&\ldots&\ldots&\beta_{2}\\
		\vdots&\vdots& &\ddots& &\vdots\\
		\beta_{N-1}&\beta_{N-1}&\ldots&\ldots&\beta_{N-1}-1&\beta_{N-1}\\
		\beta_{N}&\beta_{N}&\ldots&\ldots&\beta_{N}&\beta_{N}-1
where, without loss of generality,  we assume that the parameters satisfy
\begin{equation}\label{ratesConditions}
	\sum_{a=1}^{N}\alpha_{a}=1,\qquad\sum_{a=1}^{N}\beta_{a}=1
We define also 
\begin{equation}\label{lambdaConditions}
	\lambda_{a}=\alpha_{a}-\beta_{a}\quad\text{with}\quad \sum_{a=1}^{N}\lambda_{a}=0\,.
Under these assumption the Hamiltonian is integrable (see \cite{vanicat2017exact} for its derivation within the Quantum Inverse Scattering method). \\
\paragraph{Duality.} 

@@

In the long-time limit, the dual process voids the chain, and all particles are eventually absorbed at the extra-sites $0$ and $L+1$.
\paragraph{Matrix Product Ansatz (MPA).} The matrix product ansatz for the non-equilibrium steady state has been formulated in \cite{vanicat2017exact}, here we briefly recall it.

@@

	|\Psi\rangle=\frac{1}{Z_{L}}\langle W|\begin{pmatrix}

@@

	Z_{L}=\langle W|(X_{1}+\ldots +X_{N})^{L}|V\rangle

@@

	\langle W|\left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=\lambda_{a}\langle W|\qquad\forall a=1,\ldots,N

@@

Without loss of generality, we further assume that $\langle W|V\rangle=1$. 

@@

		\sum_{a=1}^{N}	\langle W|\left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=\sum_{a=1}^{N}\lambda_{a}\langle W|=0

@@

	\langle W|\left(\lambda_{a}\Xt_{1}-\Xt_{a}\right)=\lambda_{a}\langle W|\qquad\forall a=2,\ldots,N

@@

	|\Psi^{''}\rangle = \frac{1}{Z_{L}}\sum_{\bm{n}\in \Omega}\langle W|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}

@@

To determine the steady state \eqref{toDetermineTilde}, we need to compute the coefficient $\langle W|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{\xi_{a}^{x}}

@@

	\langle W|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
	|V \rangle=\langle W|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{l}}\prod_{x=1}^{L}\prod_{a=2}^{N}\left(\widetilde{X}_{a}+\lambda_{a}\sum_{j=x}^{L}n_{1}^{j}\right)^{n_{a}^{x}}|V\rangle

@@

	\langle W|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
	|V \rangle&=\langle W|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{x}}\prod_{x=1}^{L}\prod_{a=2}^{N}\left(\lambda_{a}+\lambda_{a}\sum_{j=x}^{L}n_{1}^{j}\right)^{n_{a}^{x}}|V\rangle
	\langle W|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{l}}\prod_{x=1}^{L}\prod_{a=2}^{N}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{1}^{j}\right)^{n_{a}^{x}}|V\rangle
	\prod_{x=1}^{L}\prod_{a=2}^{N}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{1}^{j}\right)^{n_{a}^{x}}\langle W|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{l}}|V\rangle

@@

To determine the state we need to compute $\langle W|\widetilde{X}_{1}^{\sum_{x=1}^{L}n_{1}^{l}}|V\rangle$. Calling $\sum_{x=1}^{L}n_{1}^{x}=n_{1}$ and taking an arbitrary $a\in \{2,\ldots,N\}$ we have

@@

	\langle W|\widetilde{X}_{1}^{n_{1}}|V\rangle&=\langle W|\widetilde{X}_{1}\widetilde{X}_{1}^{n_{1}-1}|V\rangle=\langle W|\widetilde{X}_{1}^{n_{1}-1}|V\rangle +\langle W|\frac{1}{\lambda_{a}}\widetilde{X}_{a}\widetilde{X}_{1}^{n_{1}-1}|V\rangle
	\langle W|\widetilde{X}_{1}^{n_{1}-1}|V\rangle+\frac{1}{\lambda_{a}}\langle W|\widetilde{X}_{1}^{n_{1}-1}\left(\widetilde{X}_{a}+\lambda_{a}(n_{1}-1)\right)|V\rangle
	\langle W|\widetilde{X}_{1}^{n_{1}-1}|V\rangle+\left(n_{1}+1-1\right)\langle W|\widetilde{X}_{1}^{n_{1}-1}|V\rangle
	\left(2+n_{1}-1\right)\langle W|\widetilde{X}_{1}^{n_{1}-1}|V\rangle
	\frac{\Gamma(2+n_{1})}{\Gamma(2+n_{1}-1)}\langle W|\widetilde{X}_{1}^{n_{1}-1}|V\rangle

@@

		\langle W|\widetilde{X}_{1}^{n_{1}}|V\rangle=\frac{\Gamma(2+n_{1})}{\Gamma(2+n_{1}-1)}\langle W|\widetilde{X}_{1}^{n_{1}-1}|V\rangle\\
		\langle W|\widetilde{X}_{1}^{0}|V\rangle=1

@@

	\langle W|\widetilde{X}_{1}^{n_{1}}|V\rangle&=\frac{\Gamma(2+n_{1})}{\Gamma(2+n_{1}-1)}\langle W|\widetilde{X}_{1}^{n_{1}-1}|V\rangle=\langle W|\widetilde{X}_{1}^{n_{1}}|V\rangle=\frac{\Gamma(2+n_{1})}{\Gamma(2+n_{1}-1)}\frac{\Gamma(2+n_{1}-1)}{\Gamma(2+n_{1}-2)}\langle W|\widetilde{X}_{1}^{n_{1}-2}|V\rangle\\&=
	\frac{\Gamma(2+n_{1})}{\Gamma(2+n_{1}-1)}\frac{\Gamma(2+n_{1}-1)}{\Gamma(2+n_{1}-2)}\ldots \frac{\Gamma(2-1)}{\Gamma(2)}\langle W|\widetilde{X}_{1}^{0}|V\rangle

@@

	\langle W|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}

@@

	Z_{L}&=\langle W|(X_{1}+\ldots+X_{N})^{L}|V\rangle=\langle W|\widetilde{X}_{1}^{L}|V|\rangle=

@@

f(L,c_{1},\ldots,c_{m})\sum_{t_{1}=0}^{c_{1}}\sum_{t_{m}=1}^{c_{m}}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}\alpha_{a_{q}}^{t_{q}}\beta_{a_{q}}^{1-t_{q}}g_{q}(L,x_{q},c_{q},\ldots,c_{m})

@@

@@

>>>>

\subsection{Integrable process on a line segment}
In this section we specialize the multi-species stirring process to the geometry of the one dimensional chain with sites $\{1,\ldots,L\}$ where two reservoirs act at the boundary sites $1$ and $L$. These boundaries, exchanging particle with the external environment, put the chain out of equilibrium. The Hamiltonian that we consider here is obtained by \eqref{OriginalHamiltonian} assuming that the conductances are
\begin{equation}
	\omega_{x,y}=\begin{cases}
		1 \quad \text{if}\quad |x-y|=1\\
		0\quad \text{otherwise}
	\end{cases}
\end{equation}
and the local inhomogeneities are
\begin{equation}
	\Gamma_{x}=\begin{cases}
		1\quad \text{if} \quad x\in \{1,L\}\\
		0\quad \text{otherwise}
	\end{cases}
\end{equation}
We further assume that the maximal occupancy in each site is $\nu=1$, i.e. that there is an \textit{hard-core interaction}.
We will denote the element of the representation of the $gl(N)$ Lie algebra by lowercase letters, i.e. $(e_{ab})_{a,b\in\{1,\ldots,N\}}$, to highlight that we are in  the fundamental representation of the algebra.
The Hamiltonian is
\begin{equation}\label{hamiltonian}
	H=H_{left}+H_{bulk}+H_{right}
\end{equation}
where
\begin{equation}
	H_{bulk}=\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}
\end{equation}
Here $\mathcal{H}_{x,x+1}$  is a copy (acting on the edge $x,x+1$) of the two-site Hamiltonian
\begin{equation}
	\begin{split}
		\mathcal{H}=P-\id
	\end{split}
\end{equation}
with 
\begin{equation}
	P=\sum_{a,b=1}^Ne_{ab}\otimes e_{ba}.
\end{equation} 
The action of $\mathcal{H}$ amounts to the permutation of the occupations the two sites, i.e.
\begin{equation}
	\begin{split}
		\mathcal{H}|n\rangle\otimes   |m\rangle&=|m\rangle \otimes |n\rangle-|n\rangle \otimes|m\rangle
	\end{split}
\end{equation}
The boundary terms are given by 
\begin{equation}
	H_{left}=\begin{pmatrix}
		\alpha_{1}-1&\alpha_{1}&\alpha_{1}&\ldots&\ldots&\alpha_{1}\\
		\alpha_{2}&\alpha_{2}-1&\alpha_{2}&\ldots&\ldots&\alpha_{2}\\
		\vdots&\vdots& &\ddots& &\vdots\\
		\alpha_{N-1}&\alpha_{N-1}&\ldots&\ldots&\alpha_{N-1}-1&\alpha_{N-1}\\
		\alpha_{N}&\alpha_{N}&\ldots&\ldots&\alpha_{N}&\alpha_{N}-1
	\end{pmatrix}
\end{equation}
\begin{equation}
	H_{right}=\begin{pmatrix}
		\beta_{1}-1&\beta_{1}&\beta_{1}&\ldots&\ldots&\beta_{1}\\
		\beta_{2}&\beta_{2}-1&\beta_{2}&\ldots&\ldots&\beta_{2}\\
		\vdots&\vdots& &\ddots& &\vdots\\
		\beta_{N-1}&\beta_{N-1}&\ldots&\ldots&\beta_{N-1}-1&\beta_{N-1}\\
		\beta_{N}&\beta_{N}&\ldots&\ldots&\beta_{N}&\beta_{N}-1
	\end{pmatrix}
\end{equation}
where, without loss of generality,  we assume that the parameters satisfy
\begin{equation}\label{ratesConditions}
	\sum_{a=1}^{N}\alpha_{a}=1,\qquad\sum_{a=1}^{N}\beta_{a}=1
\end{equation} 
We define also 
\begin{equation}\label{lambdaConditions}
	\lambda_{a}=\alpha_{a}-\beta_{a}\quad\text{with}\quad \sum_{a=1}^{N}\lambda_{a}=0\,.
\end{equation}
Under these assumption the Hamiltonian is integrable (see \cite{vanicat2017exact} for its derivation within the Quantum Inverse Scattering method).

@@

\subsection{Duality for the integrable process on a line segment}

@@

In the long-time limit, the dual process voids the chain, and all particles are eventually absorbed at the extra-sites $0$ and $L+1$.\\
In this situation the elements of the duality matrix \eqref{dualityElements} read
\begin{equation}\label{ElementsDualityMatrixChain}
	D(\bm{n},\bm{\xi})=\prod_{a=2}^{N}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=2}^{N}\mathbbm{1}_{\{n_{a}^{x}\geq \xi_{a}^{x}\}}\right)\prod_{a=2}^{N}\beta_{a}^{\xi_{a}^{L+1}}
Using the above duality elements, we can compute the  $m$-point correlations between non-empty particles using the absorption probabilities. Consider a dual configuration $\hat{\xi}:=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$ where $a_{k}\in\{2,\ldots,N\}$ and $x_{k}\in\{1,\ldots,L\}$ for every $k\in\{1,\ldots,m\}$. Considering the elements \eqref{ElementsDualityMatrixChain} of the duality matrix computed in the dual configuration $\hat{\xi}$ we obtain that, for every $\bm{n}$
	D(\bm{n},\hat{\xi})=\prod_{k=1}^{m}\mathbbm{1}_{\{n_{a_{k}}^{x_{k}}=1\}}
therefore, its expectation with respect to the steady state non-equilibrium distribution gives the $m$-points correlations. Moreover, recalling that the dual process eventually voids the chain by putting all particles in the extra-sites $0$ and $L$ we have the following chain of equalities
\begin{equation}\label{CorrelationByABS-prob}
	\langle n_{a_{1}}^{x_{1}}\cdots n_{a_{m}}^{x_{m}}\rangle_{stat}&=\mathbb{E}_{stat}\left[D(\bm{n},\hat{\xi})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{n}}\left[D(\bm{n}(t),\hat{\xi})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{n},\hat{\xi}(t))\right]
	\\&=\langle\hat{\bm{\xi}}\rangle_{stat,dual}=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{i_{k}}\beta_{a_{k}}^{1-i_{k}}\mathcal{P}(t_{1},\ldots,t_{m},\hat{\bm{\xi}})
\begin{equation}\label{absProbabilitiesIntegrable}
	\mathcal{P}(t_{1},\ldots,t_{m},\hat{\bm{\xi}}):=\mathbb{P}\left(\bm{\xi}(\infty)=\sum_{k=1}^{m}\left(t_{a}\delta_{0}+(1-t_{a})\delta_{L+1}\right)| \bm{\xi}(0)=\hat{\bm{\xi}}\right)
and they are called \textit{absorption probabilities}.
The matrix product ansatz for the non-equilibrium steady state has been formulated in \cite{vanicat2017exact}, here we briefly recall it.

@@

	|\Psi\rangle=\frac{1}{Z_{L}}\langle V^{*}|\begin{pmatrix}

@@

	Z_{L}=\langle V^{*}|(X_{1}+\ldots +X_{N})^{L}|V\rangle

@@

	\langle V^{*}|\left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=\lambda_{a}\langle V^{*}|\qquad\forall a=1,\ldots,N

@@

Without loss of generality, we further assume that $\langle V^{*}|V\rangle=1$. 

@@

		\sum_{a=1}^{N}	\langle V^{*}|\left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=\sum_{a=1}^{N}\lambda_{a}\langle V^{*}|=0

@@

	\langle V^{*}|\left(\lambda_{a}\Xt_{1}-\Xt_{a}\right)=\lambda_{a}\langle V^{*}|\qquad\forall a=2,\ldots,N

@@

	|\Psi^{''}\rangle = \frac{1}{Z_{L}}\sum_{\bm{n}\in \Omega}\langle V^{*}|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}

@@

To determine the steady state \eqref{toDetermineTilde}, we need to compute the coefficient $\langle V^{*}|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{\xi_{a}^{x}}

@@

	\langle V^{*}|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
	|V \rangle=\langle V^{*}|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{l}}\prod_{x=1}^{L}\prod_{a=2}^{N}\left(\widetilde{X}_{a}+\lambda_{a}\sum_{j=x}^{L}n_{1}^{j}\right)^{n_{a}^{x}}|V\rangle

@@

	\langle V^{*}|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}
	|V \rangle&=\langle V^{*}|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{x}}\prod_{x=1}^{L}\prod_{a=2}^{N}\left(\lambda_{a}+\lambda_{a}\sum_{j=x}^{L}n_{1}^{j}\right)^{n_{a}^{x}}|V\rangle
	\langle V^{*}|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{l}}\prod_{x=1}^{L}\prod_{a=2}^{N}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{1}^{j}\right)^{n_{a}^{x}}|V\rangle
	\prod_{x=1}^{L}\prod_{a=2}^{N}\left(\lambda_{a}\right)^{n_{a}^{x}}\left(1+\sum_{j=x}^{L}n_{1}^{j}\right)^{n_{a}^{x}}\langle V^{*}|\widetilde{X}_{1}^{\sum_{i=1}^{L}n_{1}^{l}}|V\rangle

@@

To determine the state we need to compute $\langle V^{*}|\widetilde{X}_{1}^{\sum_{x=1}^{L}n_{1}^{l}}|V\rangle$. Calling $\sum_{x=1}^{L}n_{1}^{x}=n_{1}$ and taking an arbitrary $a\in \{2,\ldots,N\}$ we have

@@

	\langle V^{*}|\widetilde{X}_{1}^{n_{1}}|V\rangle&=\langle V^{*}|\widetilde{X}_{1}\widetilde{X}_{1}^{n_{1}-1}|V\rangle=\langle V^{*}|\widetilde{X}_{1}^{n_{1}-1}|V\rangle +\langle V^{*}|\frac{1}{\lambda_{a}}\widetilde{X}_{a}\widetilde{X}_{1}^{n_{1}-1}|V\rangle
	\langle V^{*}|\widetilde{X}_{1}^{n_{1}-1}|V\rangle+\frac{1}{\lambda_{a}}\langle V^{*}|\widetilde{X}_{1}^{n_{1}-1}\left(\widetilde{X}_{a}+\lambda_{a}(n_{1}-1)\right)|V\rangle
	\langle V^{*}|\widetilde{X}_{1}^{n_{1}-1}|V\rangle+\left(n_{1}+1-1\right)\langle V^{*}|\widetilde{X}_{1}^{n_{1}-1}|V\rangle
	\left(2+n_{1}-1\right)\langle V^{*}|\widetilde{X}_{1}^{n_{1}-1}|V\rangle
	\frac{\Gamma(2+n_{1})}{\Gamma(2+n_{1}-1)}\langle V^{*}|\widetilde{X}_{1}^{n_{1}-1}|V\rangle

@@

		\langle V^{*}|\widetilde{X}_{1}^{n_{1}}|V\rangle=\frac{\Gamma(2+n_{1})}{\Gamma(2+n_{1}-1)}\langle V^{*}|\widetilde{X}_{1}^{n_{1}-1}|V\rangle\\
		\langle V^{*}|\widetilde{X}_{1}^{0}|V\rangle=1

@@

	\langle V^{*}|\widetilde{X}_{1}^{n_{1}}|V\rangle&=\frac{\Gamma(2+n_{1})}{\Gamma(2+n_{1}-1)}\langle V^{*}|\widetilde{X}_{1}^{n_{1}-1}|V\rangle=\langle V^{*}|\widetilde{X}_{1}^{n_{1}}|V\rangle=\frac{\Gamma(2+n_{1})}{\Gamma(2+n_{1}-1)}\frac{\Gamma(2+n_{1}-1)}{\Gamma(2+n_{1}-2)}\langle V^{*}|\widetilde{X}_{1}^{n_{1}-2}|V\rangle\\&=
	\frac{\Gamma(2+n_{1})}{\Gamma(2+n_{1}-1)}\frac{\Gamma(2+n_{1}-1)}{\Gamma(2+n_{1}-2)}\ldots \frac{\Gamma(2-1)}{\Gamma(2)}\langle V^{*}|\widetilde{X}_{1}^{0}|V\rangle

@@

	\langle V^{*}|\prod_{x=1}^{L}\prod_{a=1}^{N}\widetilde{X}_{a}^{n_{a}^{x}}

@@

	Z_{L}&=\langle V^{*}|(X_{1}+\ldots+X_{N})^{L}|V\rangle=\langle V^{*}|\widetilde{X}_{1}^{L}|V|\rangle=

@@

f(L,c_{1},\ldots,c_{m})\sum_{t_{1}=0}^{c_{1}}\ldots\sum_{t_{m}=0}^{c_{m}}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}\alpha_{a_{q}}^{t_{q}}\beta_{a_{q}}^{1-t_{q}}g_{q}(L,x_{q},c_{q},\ldots,c_{m})
By exchanging the summations we rewrite it as 
\langle n^{x_{1}}_{a_{1}}\cdots n^{x_{m}}_{a_{m}}\rangle_{\text{stat}}=\sum_{t_{1},\ldots,t_{m}=0}^{1}
\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}\alpha_{a_{q}}^{t_{q}}\beta_{a_{q}}^{1-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,x_{q},c_{q},\ldots,c_{m})
Therefore, comparing this formula and \eqref{absProbabilitiesIntegrable}, we can determine the absorption probabilities 
	\mathcal{P}(t_{1},\ldots,t_{m},\hat{\bm{\xi}})=\sum_{c_{1}=t_{1}}^{1}\ldots\sum_{c_{m}=t_{m}}^{1}\prod_{q=1}^{m}(-1)^{c_{q}-t_{q}}f(L,c_{1},\ldots,c_{m})g_{q}(L,x_{q},c_{q},\ldots,c_{m})
where $\hat{\bm{\xi}}=\sum_{i=1}^{m}\delta_{a_{i}}^{x_{i}}$. 
This means that the $m$-point correlations can also be written in terms of these absorption probabilities. 

@@

\paragraph{Proof of formula \eqref{exactCorrelations}} Consider $m$ particles of non-empty types $a_{i}\in\{2,\ldots,N\}$ in positions $x_{i}\in\{1,\ldots,L\}$ for all $i=1,\ldots,m$. We aim to compute the non-equilibrium stationary state correlation $\langle n_{a_{1}}^{x_{1}}\cdots n_{a_{m}}^{x_{m}} \rangle_{stat}$. By using duality, we showed in \eqref{CorrelationByABS-prob} that
 	\langle n_{a_{1}}^{x_{1}}\cdots n_{a_{m}}^{x_{m}} \rangle_{stat}=\langle\hat{\bm{\xi}}\rangle_{stat,dual}
Using formula \eqref{ABS} for a configuration where all $\tau_{i}$ are non-empty species, we obtain that 
	\langle n_{a_{1}}^{x_{1}}\cdots n_{a_{m}}^{x_{m}} \rangle_{stat}=\langle\hat{\bm{\xi}}\rangle_{stat,dual}=\sum_{c_{1}=0}^{1}\ldots\sum_{c_{L}=0}^{1}\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{k})}{\Gamma(2+L)}\prod_{k=1}^{m}\lambda_{\tau_{k}}^{c_{k}}\beta_{\tau_{k}}^{1-c_{k}}\left(2+L-x_{k}-\sum_{j=k}^{m}c_{j}\right)^{c_{k}}

@@

\end{flushright}}
